---
title: "Lab 7"
author: "Deanna Elliott"
date: "11/9/2021"
output: html_document
---

```{r setup, include=TRUE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

library(tidyverse)
library(palmerpenguins)
library(GGally)
library(broom)
library(kableExtra)
library(modelsummary)
library(stargazer)
```

## Explore Penguins Dataset

Use 'GGally::ggpairs()' to create a pairs plot

```{r}

ggpairs(penguins)
```

That's kind of overkill. Let's simplify the variables that we include in our ggpairs plot:

- species
- bill_length_mm through body_mass_g

```{r}

penguins %>% 
  select(species, bill_length_mm:body_mass_g) %>% 
  ggpairs(aes(color = species))
```

## Multiple Linear Regression

We going to try to understand a bit better the relationships between multiple predictor variables and an outcome variable which is penguin body mass.

The different predictor variables we're going to try are:

- species
- flipper length
- sex
- bill depth

### Model 1

Model body mass based only on flipper length and bill depth (bad idea... there are important variables missing)

```{r}

model_1 <- lm(body_mass_g ~ flipper_length_mm + bill_depth_mm, data = penguins)

# call model_1 to return only coefficients
model_1

# more information on coefficients and stats
summary(model_1)
```

Flipper length coefficient: If everything else is held constant, we expect that for each 1 mm increase in flipper length, penguin body mass is expected to increase by 51.54 g, on average.

R2 = 0.76: 76% of the variance in penguin body mass is explained by this model, which contains flipper length and bill depth.

Actually -- we think that a model for penguin body mass should contain variables species, flipper length, and sex.

```{r}

model_2 = lm(body_mass_g ~ species + flipper_length_mm + sex, data = penguins)

summary(model_2)
```

References:

- Species = Adelie
- Sex = Female

Try interpreting coefficients for flipper length, Gentoo, and male

- Flipper length: For every 1 mm increase in flipper length, we would expect, on average, a 20 g increase in body mass if all other variables are held constant.
- Gentoo: If all other variables are held constant, if a penguin is Gentoo, we would expect it to be 836 g larger in body mass, on average, than an Adelie that is otherwise similar.
- Male: On average, we expect a male penguin to be 530 g larger in body mass than a female, if all other variables are held constant.

mass (g) = 366 + 20(flipper length) - 88(Chinstrap) + 836(Gentoo) + 530(male)

## Visualize this model

```{r}
ggplot(data = penguins, 
       aes(x = flipper_length_mm, y = body_mass_g)) +
  geom_point(aes(color = species)) +
  facet_wrap(~ sex)
```

## A couple ways to get and report MLR model outcomes

Use broom::tidy() to get model coefficient info into tidy format

```{r}

penguin_model2_coef <- tidy(model_2)
```

Try to write inline code `r` that returns the coefficient for Gentoo:

`r penguin_model2_coef$estimate[3]`

## Look at model diagnostics

Use the plot() function

```{r}

plot(model_2)

summary(model_2)
```

R2 = 0.87: 87% of the variance in penguin body mass is explained by this model, which contains flipper length, species, and sex.

## Report the model outputs in a summary table

Use modelsummary()

```{r}

modelsummary(model_2)
```


Use stargazer

```{r, results = "asis"}

stargazer(model_2, type = "html")
```

